A state space model reveals the rich and varied dynamics of hippocampal replay

### 2020-07-21 Article.tex
Update on Overleaf.

\subsection*{Software and Code Availability}
Python code used for analysis and generating figures in the paper is available at: \url{https://github.com/Eden-Kramer-Lab/replay_trajectory_paper}. Code for the classifier is available in a separate software repository to facilitate code reuse at: \url{https://github.com/Eden-Kramer-Lab/replay_trajectory_classification}.
Both code bases rely on the following python packages: Numpy \cite{vanderWaltNumPyArrayStructure2011}, Numba \cite{LamNumbaLLVMbasedPython2015}, Matplotlib \cite{HunterMatplotlib2DGraphics2007}, xarray \cite{HoyerxarrayNDlabeled2017}, NetworkX \cite{HagbergExploringNetworkStructure2008}, Pandas \cite{McKinneyDataStructuresStatistical2010} and Seaborn (doi: 10.5281/zenodo.883859). All code is open-source and licensed under the MIT Software License. Classifier code can be easily installed as a python package with all requisite dependencies using pip or conda. See software repositories for specific details.

>>>>

\subsection*{Software and Code Availability}
Python code used for analysis and generating figures in the paper is available at: \url{https://github.com/Eden-Kramer-Lab/replay_trajectory_paper}. Code for the classifier is available in a separate software repository to facilitate code reuse at: \url{https://github.com/Eden-Kramer-Lab/replay_trajectory_classification} ((doi: 10.5281/zenodo.3713412).
Both code bases rely on the following python packages: Numpy \cite{vanderWaltNumPyArrayStructure2011}, Numba \cite{LamNumbaLLVMbasedPython2015}, Matplotlib \cite{HunterMatplotlib2DGraphics2007}, xarray \cite{HoyerxarrayNDlabeled2017}, NetworkX \cite{HagbergExploringNetworkStructure2008}, Pandas \cite{McKinneyDataStructuresStatistical2010} and Seaborn (doi: 10.5281/zenodo.883859). All code is open-source and licensed under the MIT Software License. Classifier code can be easily installed as a python package with all requisite dependencies using pip or conda. See software repositories for specific details.
